---
output: cynkratemplate::readme_document
---

<!-- README.md is generated from README.Rmd. Please edit that file. -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/dropin-",
  out.width = "100%"
)

clean_output <- function(x, options) {
  x <- gsub("0x[0-9a-f]+", "0xdeadbeef", x)
  x <- gsub("dataframe_[0-9]*_[0-9]*", "      dataframe_42_42      ", x)
  x <- gsub("[0-9]*\\.___row_number ASC", "42.___row_number ASC", x)
  x
}

options(
  cli.num_colors = 256,
  cli.width = 71,
  width = 71,
  pillar.bold = TRUE,
  pillar.max_title_chars = 5,
  pillar.min_title_chars = 5,
  pillar.max_footer_lines = 12,
  conflicts.policy = list(warn = FALSE)
)

local({
  hook_source <- knitr::knit_hooks$get("document")
  knitr::knit_hooks$set(document = clean_output)
})

help <- function(...) {
  x <- utils::help(...)
  y <- utils:::.getHelpFile(x)
  z <- capture.output(tools::Rd2txt(y))
  out <- paste0("```\n", paste(gsub("_.", "", z), collapse = "\n"), "\n```")
  knitr::asis_output(out)
}
```

# dd

<!-- badges: start -->
`r sprintf("[![DuckDB](https://img.shields.io/badge/DuckDB-%s-FFF000?logo=duckdb&logoColor=black)](https://duckdb.org)", sub("^v", "", duckdb::sql_query("PRAGMA version")$library_version))`
<!-- badges: end -->

The goal of dd is to provide documentation for DuckDB's functions, and later also an easy way to test them.
It is meant to be used in conjunction with [duckplyr](https://duckplyr.tidyverse.org/) and [duckdb](https://duckdb.org/docs/stable/clients/r).

`r sprintf("These pages document the functions of **DuckDB %s**.", sub("^v", "", duckdb::sql_query("PRAGMA version")$library_version))`


## Goals and non-goals

dd aims to:

- Give every DuckDB function a help page in R, so `?acos` and `help(acos, package = "dd")` work from the R console.
- Describe each function as DuckDB does: argument names and types, return type, overloads, SQL examples, and the extension that provides it.
- Cover the DuckDB build it was generated from, including the functions DuckDB's core extensions add.
- Make the same set of names reachable through the `dd` list, so a function can be looked up by name as well as with `?`.
- Install with nothing but R itself: the package declares no `Imports` and no `Suggests`.

It is explicitly not trying to:

- Run DuckDB functions in R. Every stub errors with `DuckDB function acos() is not available in R.`
- Stand in for duckplyr or the duckdb R client; dd is meant to be used alongside them.
- Shadow the base R functions it documents. `format()`, `length()`, `+` and `-` get a help page but are deliberately not exported.
- Document DuckDB's internals. Function names beginning with `__` are dropped.
- Reach past DuckDB's core extension repository. Extensions are installed `FROM core`, so community extensions are never documented.

## Installation

You can install the development version of dd like so:

``` r
pak::pak("cynkra/dd")
```

## Example

```{r example}
library(dd)
dd$acos

help(acos, package = "dd")
```
